Analysis of Bauer et al. (unpublished) Field experiment: <br> Recovery completeness

### 2022-12-16 R/model_recovery_check.Rmd
Update model_recovery_check.Rmd

```{r analysis-preparation}
# Chose variables
variables <- c(
      "Intercept",
      "b_sand_ratio25",
      "b_sand_ratio50",
      "b_substrate_depth15",
      "b_target_typedry_grassland",
      "b_seed_density8",
      "b_expositionsouth",
      "b_survey_year_fct2019",
      "b_survey_year_fct2020",
      "b_survey_year_fct2021",
      "sd_site__Intercept",
      "sd_site:plot__Intercept",
      "sigma"
    )
# Subset draws
posterior1 <- m_1 %>%
  posterior::as_draws() %>%
  posterior::subset_draws(variable = variables)
posterior2 <- m_2 %>%
  posterior::as_draws() %>%
  posterior::subset_draws(variable = variables)
posterior_prior <- m_prior %>%
  posterior::as_draws() %>%
  posterior::subset_draws(variable = variables)
posterior_flat <- m_flat %>%
  posterior::as_draws() %>%
  posterior::subset_draws(variable = variables)
# R hat
rhat1 <- rhat(m_1)
rhat2 <- rhat(m_2)
# NEFF ratio
neff1 <- neff_ratio(m_1)
neff2 <- neff_ratio(m_2)
# Long format of draws
hmc_diagnostics1 <- brms::nuts_params(m_1)
hmc_diagnostics2 <- brms::nuts_params(m_2)
y <- sites$n
# Posterior predictive distribution
yrep1 <- brms::posterior_predict(m_1, draws = 500)
yrep2 <- brms::posterior_predict(m_2, draws = 500)
yrep_prior <- brms::posterior_predict(m_prior, draws = 500)
# Leave-one-out cross validation based on posterior likelihood
loo1 <- brms::loo(m_1, save_psis = TRUE, moment_match = FALSE)
loo2 <- brms::loo(m_2, save_psis = TRUE, moment_match = FALSE)
# Summary statistics
draws1 <- m_1 %>%
  posterior::as_draws() %>%
  posterior::summarize_draws() %>%
  filter(str_starts(variable, "b_"))
draws2 <- m_2 %>%
  posterior::as_draws() %>%
  posterior::summarize_draws() %>%
  filter(str_starts(variable, "b_"))
```

@@

```{r prior-predictive-check}
ppd_stat(yrep_prior[1:500, ], binwidth = 0.2) +
  coord_cartesian(xlim = c(-2, 2))
ppd_stat_grouped(yrep_prior[1:500, ], group = sites$site,
                 binwidth = 0.2) +
  coord_cartesian(xlim = c(-2, 2))
ppd_stat_grouped(yrep_prior[1:500, ], group = sites$exposition,
                 binwidth = 0.2) +
  coord_cartesian(xlim = c(-2, 2))
ppd_stat_grouped(yrep_prior[1:500, ], group = sites$survey_year_fct,
                 binwidth = 0.2) +
  coord_cartesian(xlim = c(-2, 2))
ppd_stat_grouped(yrep_prior[1:500, ], group = sites$target_type,
                 binwidth = 0.2) +
  coord_cartesian(xlim = c(-2, 2))
ppd_stat_grouped(yrep_prior[1:500, ], group = sites$seed_density,
                 binwidth = 0.1) +
  coord_cartesian(xlim = c(-2, 2))
ppd_stat_grouped(yrep_prior[1:500, ], group = sites$sand_ratio,
                 binwidth = 0.2) +
  coord_cartesian(xlim = c(-2, 2))
ppd_stat_grouped(yrep_prior[1:500, ], group = sites$substrate_depth,
                 binwidth = 0.2) +
  coord_cartesian(xlim = c(-2, 2))
```

@@

```{r rhat, collapse = TRUE}
mcmc_rhat(rhat1)
mcmc_rhat(rhat2)
```

@@

```{r ess, collapse = TRUE}
mcmc_neff(neff1)
mcmc_neff(neff2)
```

@@

```{r mcmc-trace, fig.height = 14}
mcmc_trace(posterior1, np = hmc_diagnostics1, facet_args = list(ncol = 2))
mcmc_trace(posterior2, np = hmc_diagnostics2, facet_args = list(ncol = 2))
```

@@

```{r mcmc-pairs, collapse = TRUE, fig.height = 6.5}
mcmc_pairs(m_1, off_diag_args = list(size = 1.2),
           pars = c(
             "b_sand_ratio25", "b_sand_ratio50", "b_substrate_depth15",
             "b_target_typedry_grassland", "b_seed_density8",
             "b_expositionsouth", "sigma"
           ))
mcmc_pairs(m_2, off_diag_args = list(size = 1.2),
           pars = c(
             "b_sand_ratio25", "b_sand_ratio50", "b_substrate_depth15",
             "b_target_typedry_grassland", "b_seed_density8",
             "b_expositionsouth", "sigma"
           ))
```

@@

```{r mcmc-parcoord, collapse = TRUE}
mcmc_parcoord(posterior1, np = hmc_diagnostics1) +
  theme(axis.text.x = element_text(angle = 45))
mcmc_parcoord(posterior2, np = hmc_diagnostics2) +
  theme(axis.text.x = element_text(angle = 45))
```

@@

```{r kernel-density}
p1 <- ppc_dens_overlay(y, yrep1[1:50, ])
p2 <- ppc_dens_overlay(y, yrep2[1:50, ])
p1 / p2
ppc_dens_overlay_grouped(y, yrep1[1:50, ], group = sites$site)
ppc_dens_overlay_grouped(y, yrep2[1:50, ], group = sites$site)
p1 <- ppc_dens_overlay_grouped(y, yrep1[1:50, ], group = sites$exposition)
p2 <- ppc_dens_overlay_grouped(y, yrep2[1:50, ], group = sites$exposition)
p1 / p2
ppc_dens_overlay_grouped(y, yrep1[1:50, ], group = sites$survey_year_fct)
ppc_dens_overlay_grouped(y, yrep2[1:50, ], group = sites$survey_year_fct)
p1 <- ppc_dens_overlay_grouped(y, yrep1[1:50, ], group = sites$target_type)
p2 <- ppc_dens_overlay_grouped(y, yrep2[1:50, ], group = sites$target_type)
p1 / p2
p1 <- ppc_dens_overlay_grouped(y, yrep1[1:50, ], group = sites$seed_density)
p2 <- ppc_dens_overlay_grouped(y, yrep2[1:50, ], group = sites$seed_density)
p1 / p2
p1 <- ppc_dens_overlay_grouped(y, yrep1[1:50, ], group = sites$sand_ratio)
p2 <- ppc_dens_overlay_grouped(y, yrep2[1:50, ], group = sites$sand_ratio)
p1 / p2
p1 <- ppc_dens_overlay_grouped(y, yrep1[1:50, ], group = sites$substrate_depth)
p2 <- ppc_dens_overlay_grouped(y, yrep2[1:50, ], group = sites$substrate_depth)
p1 / p2
```

@@

```{r histograms}
p1 <- ppc_stat(y, yrep1, binwidth = 0.001)
p2 <- ppc_stat(y, yrep2, binwidth = 0.001)
p1 / p2
ppc_stat_grouped(y, yrep1, group = sites$site, binwidth = 0.001)
ppc_stat_grouped(y, yrep2, group = sites$site, binwidth = 0.001)
p1 <- ppc_stat_grouped(y, yrep1, group = sites$exposition, binwidth = 0.001)
p2 <- ppc_stat_grouped(y, yrep2, group = sites$exposition, binwidth = 0.001)
p1 / p2
ppc_stat_grouped(y, yrep1, group = sites$survey_year_fct, binwidth = 0.001)
ppc_stat_grouped(y, yrep2, group = sites$survey_year_fct, binwidth = 0.001)
p1 <- ppc_stat_grouped(y, yrep1, group = sites$target_type, binwidth = 0.001)
p2 <- ppc_stat_grouped(y, yrep2, group = sites$target_type, binwidth = 0.001)
p1 / p2
p1 <- ppc_stat_grouped(y, yrep1, group = sites$seed_density, binwidth = 0.001)
p2 <- ppc_stat_grouped(y, yrep2, group = sites$seed_density, binwidth = 0.001)
p1 / p2
p1 <- ppc_stat_grouped(y, yrep1, group = sites$sand_ratio, binwidth = 0.001)
p2 <- ppc_stat_grouped(y, yrep2, group = sites$sand_ratio, binwidth = 0.001)
p1 / p2
p1 <- ppc_stat_grouped(y, yrep1, group = sites$substrate_depth, binwidth = 0.001)
p2 <- ppc_stat_grouped(y, yrep2, group = sites$substrate_depth, binwidth = 0.001)
p1 / p2
```

>>>>

```{r analysis-preparation}
# Chose variables
variables <- c(
      "Intercept",
      "b_sand_ratio25",
      "b_sand_ratio50",
      "b_substrate_depth15",
      "b_target_typedry_grassland",
      "b_seed_density8",
      "b_expositionsouth",
      "b_survey_year_fct2019",
      "b_survey_year_fct2020",
      "b_survey_year_fct2021",
      "sd_site__Intercept",
      "sd_site:plot__Intercept",
      "sigma"
    )
# Subset draws
posterior1 <- m_1 %>%
  posterior::as_draws() %>%
  posterior::subset_draws(variable = variables)
posterior2 <- m_2 %>%
  posterior::as_draws() %>%
  posterior::subset_draws(variable = variables)
posterior_prior <- m_prior %>%
  posterior::as_draws() %>%
  posterior::subset_draws(variable = variables)
posterior_flat <- m_flat %>%
  posterior::as_draws() %>%
  posterior::subset_draws(variable = variables)
# R hat
rhat1 <- brms::rhat(m_1)
rhat2 <- brms::rhat(m_2)
# NEFF ratio
neff1 <- brms::neff_ratio(m_1)
neff2 <- brms::neff_ratio(m_2)
# Long format of draws
hmc_diagnostics1 <- brms::nuts_params(m_1)
hmc_diagnostics2 <- brms::nuts_params(m_2)
y <- sites$n
# Posterior predictive distribution
yrep1 <- brms::posterior_predict(m_1, draws = 500)
yrep2 <- brms::posterior_predict(m_2, draws = 500)
yrep_prior <- brms::posterior_predict(m_prior, draws = 500)
# Leave-one-out cross validation based on posterior likelihood
loo1 <- brms::loo(m_1, save_psis = TRUE, moment_match = FALSE)
loo2 <- brms::loo(m_2, save_psis = TRUE, moment_match = FALSE)
# Summary statistics
draws1 <- m_1 %>%
  posterior::as_draws() %>%
  posterior::summarize_draws() %>%
  filter(str_starts(variable, "b_"))
draws2 <- m_2 %>%
  posterior::as_draws() %>%
  posterior::summarize_draws() %>%
  filter(str_starts(variable, "b_"))
```

@@

```{r prior-predictive-check}
bayesplot::ppd_stat(yrep_prior[1:500, ], binwidth = 0.2) +
  coord_cartesian(xlim = c(-2, 2))
ppd_stat_grouped(yrep_prior[1:500, ], group = sites$site,
                 binwidth = 0.2) +
  coord_cartesian(xlim = c(-2, 2))
ppd_stat_grouped(yrep_prior[1:500, ], group = sites$exposition,
                 binwidth = 0.2) +
  coord_cartesian(xlim = c(-2, 2))
ppd_stat_grouped(yrep_prior[1:500, ], group = sites$survey_year_fct,
                 binwidth = 0.2) +
  coord_cartesian(xlim = c(-2, 2))
ppd_stat_grouped(yrep_prior[1:500, ], group = sites$target_type,
                 binwidth = 0.2) +
  coord_cartesian(xlim = c(-2, 2))
ppd_stat_grouped(yrep_prior[1:500, ], group = sites$seed_density,
                 binwidth = 0.1) +
  coord_cartesian(xlim = c(-2, 2))
ppd_stat_grouped(yrep_prior[1:500, ], group = sites$sand_ratio,
                 binwidth = 0.2) +
  coord_cartesian(xlim = c(-2, 2))
ppd_stat_grouped(yrep_prior[1:500, ], group = sites$substrate_depth,
                 binwidth = 0.2) +
  coord_cartesian(xlim = c(-2, 2))
```

@@

```{r rhat, collapse = TRUE}
bayesplot::mcmc_rhat(rhat1)
bayesplot::mcmc_rhat(rhat2)
```

@@

```{r ess, collapse = TRUE}
bayesplot::mcmc_neff(neff1)
bayesplot::mcmc_neff(neff2)
```

@@

```{r mcmc-trace, fig.height = 14}
bayesplot::mcmc_trace(
  posterior1, np = hmc_diagnostics1, facet_args = list(ncol = 2)
  )
bayesplot::mcmc_trace(
  posterior2, np = hmc_diagnostics2, facet_args = list(ncol = 2)
  )
```

@@

```{r mcmc-pairs, collapse = TRUE, fig.height = 6.5}
bayesplot::mcmc_pairs(m_1, off_diag_args = list(size = 1.2),
           pars = c(
             "b_sand_ratio25", "b_sand_ratio50", "b_substrate_depth15",
             "b_target_typedry_grassland", "b_seed_density8",
             "b_expositionsouth", "sigma"
           ))
bayesplot::mcmc_pairs(m_2, off_diag_args = list(size = 1.2),
           pars = c(
             "b_sand_ratio25", "b_sand_ratio50", "b_substrate_depth15",
             "b_target_typedry_grassland", "b_seed_density8",
             "b_expositionsouth", "sigma"
           ))
```

@@

```{r mcmc-parcoord, collapse = TRUE}
bayesplot::mcmc_parcoord(posterior1, np = hmc_diagnostics1) +
  theme(axis.text.x = element_text(angle = 45))
bayesplot::mcmc_parcoord(posterior2, np = hmc_diagnostics2) +
  theme(axis.text.x = element_text(angle = 45))
```

@@

```{r kernel-density}
p1 <- bayesplot::ppc_dens_overlay(y, yrep1[1:50, ])
p2 <- bayesplot::ppc_dens_overlay(y, yrep2[1:50, ])
p1 / p2
ppc_dens_overlay_grouped(y, yrep1[1:50, ], group = sites$site)
ppc_dens_overlay_grouped(y, yrep2[1:50, ], group = sites$site)
p1 <- ppc_dens_overlay_grouped(y, yrep1[1:50, ], group = sites$exposition)
p2 <- ppc_dens_overlay_grouped(y, yrep2[1:50, ], group = sites$exposition)
p1 / p2
ppc_dens_overlay_grouped(y, yrep1[1:50, ], group = sites$survey_year_fct)
ppc_dens_overlay_grouped(y, yrep2[1:50, ], group = sites$survey_year_fct)
p1 <- ppc_dens_overlay_grouped(y, yrep1[1:50, ], group = sites$target_type)
p2 <- ppc_dens_overlay_grouped(y, yrep2[1:50, ], group = sites$target_type)
p1 / p2
p1 <- ppc_dens_overlay_grouped(y, yrep1[1:50, ], group = sites$seed_density)
p2 <- ppc_dens_overlay_grouped(y, yrep2[1:50, ], group = sites$seed_density)
p1 / p2
p1 <- ppc_dens_overlay_grouped(y, yrep1[1:50, ], group = sites$sand_ratio)
p2 <- ppc_dens_overlay_grouped(y, yrep2[1:50, ], group = sites$sand_ratio)
p1 / p2
p1 <- ppc_dens_overlay_grouped(y, yrep1[1:50, ], group = sites$substrate_depth)
p2 <- ppc_dens_overlay_grouped(y, yrep2[1:50, ], group = sites$substrate_depth)
p1 / p2
```

@@

```{r histograms}
p1 <- bayesplot::ppc_stat(y, yrep1, binwidth = 0.001)
p2 <- bayesplot::ppc_stat(y, yrep2, binwidth = 0.001)
p1 / p2
ppc_stat_grouped(y, yrep1, group = sites$site, binwidth = 0.001)
ppc_stat_grouped(y, yrep2, group = sites$site, binwidth = 0.001)
p1 <- ppc_stat_grouped(y, yrep1, group = sites$exposition, binwidth = 0.001)
p2 <- ppc_stat_grouped(y, yrep2, group = sites$exposition, binwidth = 0.001)
p1 / p2
ppc_stat_grouped(y, yrep1, group = sites$survey_year_fct, binwidth = 0.001)
ppc_stat_grouped(y, yrep2, group = sites$survey_year_fct, binwidth = 0.001)
p1 <- ppc_stat_grouped(y, yrep1, group = sites$target_type, binwidth = 0.001)
p2 <- ppc_stat_grouped(y, yrep2, group = sites$target_type, binwidth = 0.001)
p1 / p2
p1 <- ppc_stat_grouped(y, yrep1, group = sites$seed_density, binwidth = 0.001)
p2 <- ppc_stat_grouped(y, yrep2, group = sites$seed_density, binwidth = 0.001)
p1 / p2
p1 <- ppc_stat_grouped(y, yrep1, group = sites$sand_ratio, binwidth = 0.001)
p2 <- ppc_stat_grouped(y, yrep2, group = sites$sand_ratio, binwidth = 0.001)
p1 / p2
p1 <- ppc_stat_grouped(y, yrep1, group = sites$substrate_depth, binwidth = 0.001)
p2 <- ppc_stat_grouped(y, yrep2, group = sites$substrate_depth, binwidth = 0.001)
p1 / p2
```
